Improving Usability of Remote Access to Sensitive Data

### 2014-07-21 ccsw14/paper.tex
added to related work

\title{Improving the Usability of Remote Access to Sensitive Data}

\author{
Draft Copy
}

@@

One good example of a system for access to sensitive data is the data for the
United States Census.  The federal government established Census Research Data
Centers (RDCs) to enable researchers access to unpublished Census data for the
purpose of conducting research that could provide beneficial guidance to public
policy.  Once granted access, a researcher must visit one of the CRDCs in
person, and will then be permitted to use preallocated machines with preloaded
software in order to conduct their research.  Upon completion of their research,
their results are human-audited to protect confidentiality, and then released.
While this system provides access to Census data, and seems robust to data
leaks, it is also highly restrictive, requiring researchers to relocate and use
foreign hardware to conduct research.

More recently, the Centers for Medicare and Medicaid Services began providing
Medicare and Medicaid data using the CMS Virtual Research Data Center (VRDC) in
2013.  VRDC provides a more flexible model by allowing researchers to remotely
access desktop environments provided by a cloud infrastructure.  This model
relieves researchers of the need to travel to a physical location, and also
avoids the security risk of researchers having to receive and safeguard physical
copies of the data, while they are conducting their research.

@@

@@

\subsection{Security Guarantees and Threat Model}

>>>>

\title{Improving Usability of Remote Access to Sensitive Data}

\author{
Draft Copy: \today
}

@@

% Mention state of the art for supervised research

@@

\subsection{Real-World Systems}

Systems that enable supervised and audited computational research of sensitive
data date back at least as far as the 1990s, when a Census Research Data Center
was opened in Boston.  Since the opening of this initial office, the U.S.
federal government has established several Research Data Centers (RDCs) across
the country to enable researchers access to unpublished Census data for the
purpose of conducting research that could provide beneficial guidance to public
policy.

Potential researchers must first submit a research proposal demonstrating
scientific merit and potential benefit to Census Bureau programs.  Once granted
access, a researcher then visits one of the CRDCs in person, and, after swearing
to protect data confidentiality, will then be permitted to use preallocated
machines inside the facility with a preloaded suite of software in order to
conduct their research.  Upon completion of their research, their results are
human-audited to protect confidentiality, and then released.

While this system provides access to Census data, and seems robust to data
leaks, it is also highly restrictive, requiring researchers to relocate and use
foreign hardware and potentially software as well, to conduct their research.

More recently, the Centers for Medicare and Medicaid Services began providing
Medicare and Medicaid data using the CMS Virtual Research Data Center (VRDC) in
2013.  VRDC provides a more flexible model by allowing researchers to remotely
access desktop environments provided by a cloud infrastructure.  This model
relieves researchers of the need to travel to a physical location, and also
avoids the security risk of researchers having to receive and safeguard physical
copies of the data while they are conducting their research, as was formerly the
case.

However, this state-of-the-art solution still suffers from significant
drawbacks, in that researchers are largely limited to using the preallocated
environments supplied by the VRDCs.  In order to upload software or data not
already available in a virtual desktop, it must first undergo a manual review
process.  For large software suites, this can at best add significant
inconvenience, and at worst expose the system to a malicious attack, as there is
no method for reliably detecting malicious software.  Data Capsules is designed
so that no review process is necessary to upload software or data to an
environment, while providing strong guarantees of data privacy by design.

\subsection{Systems Using Virtualization}

% storage capsules, QubesOS

\subsection{Information Flow Control}

% HiStar

@@

\subsection{Security Goals and Threat Model}
